Home

### 2025-07-21 index.qmd
Fix titles across multiple lines

Chancellor's Distinguished Professor of Statistics  
Statistics Department Chair, 2009 - 2012  
Professor of Electrical Engineering and Computer Sciences, by courtesy

>>>>

CDSS Chancellor's Distinguished Professor of Statistics
Electrical Engineering and Computer Sciences, and Center for Computational Biology
Statistics Department Chair, 2009 - 2012
